Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2012-10-18 documents/mixtures/mixture_models.tex
notes to self

...Show plots demonstrating quality of fit, one-d and two-d plots...

...give tables of results, including Bundy versions and recommended
versions...Why are we giving and plotting root-variances not
variances?...

...show dependence of amplitudes and variances on sersic n for some
M...be sure to synchronize $\xi_{\max}$...

>>>>

The results of the optimizations are shown in the \tablename\ and
\figurename s... Discuss briefly the import of it all... Why in the
tables are we giving and plotting root-variances not variances?...

...make recommendations: Use the $M^{\lux}=6$ lux and the $M^{\luv}=8$
luv!...
